Fully Automatic Loop-free Program Synthesis by Bounded Model Checking

### 2013-10-11 paper/paper.tex
Change "automated" symbol from tick to cross
Classical allusions

\usepackage{listings}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage{pgf}
\usepackage[noend]{algpseudocode}
\usepackage{algorithm}
\usepackage{amsfonts}

@@

@@

Program synthesis is the mechanized construction of software that provably
satisfies a given specification.  Synthesis tools promise to relieve the
programmer from thinking about \emph{how} the problem is to be solved;
instead, the programmer only provides a compact description of \emph{what}
is to be achieved.  Foundational research in this area has been
exceptionally fruitful, beginning with Alonzo Church's work on the
\emph{Circuit Synthesis Problem} in the sixties~\cite{church-synth}.

@@

>>>>

\usepackage{listings}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage{pgf}
\usepackage[noend]{algpseudocode}
\usepackage{algorithm}
\usepackage{amsfonts}
\usepackage{pifont}

@@

\newcommand{\xmark}{\ding{55}}

@@

Program synthesis is the mechanized construction of software that provably
satisfies a given specification.  Synthesis tools promise to relieve the
programmer from thinking about \emph{how} the problem is to be solved;
instead, the programmer only provides a compact description of \emph{what}
is to be achieved.  Foundational research in this area has been
exceptionally fruitful, beginning with Alonzo Church's work on the
\emph{Circuit Synthesis Problem} in the sixties~\cite{church-synth}.
Since then the program synthesis problem for programs has been attacked by Manna
and Waldinger using theorem provers~\cite{manna-waldinger}, and by
Kraan et al. using proof planning techniques~\cite{proof-planning}.

@@

\paragraph{Acknowledgements}
We thank Martin Brain for his insight and advice during our synthesis discussions.
